---
title: "HBF run analysis"
output: html_document
date: "2026-05-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing packages
```{r}
packages <- c('mclust',
              'readr',
              'RCurl',
              'here',
              'tidyverse',
              'rvest',
              'dplyr',
              'hms',
              'hrbrthemes',
              'mclust',
              'knitr')
# Only installs packages if required
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)){
  install.packages(packages[!installed_packages])
}
# Importing packages
invisible(lapply(packages, library, character.only = TRUE))
```


## Scraping the data from the results website

```{r}
pages <- list()
# Base URL -> There are many pages as denoted at the end of the URL
url_pre <- "https://bluechipresults.com.au/results.aspx?CId=11&RId=1975&EId=1&dt=0&PageNo="

# Looping through all pages, creating the URLs and then scraping the data table
for (i in 1:360){
  url <- paste(url_pre, i, sep = "")
  print(url)
  popNodes <- html_nodes(read_html(url), "table")
  pop <- html_table(popNodes, header = TRUE, fill = TRUE)[[2]]
  pages[[i]] <- pop
  
}

# Merging all page data into one df
df <- bind_rows(pages)
```

Saving initial CSV as hbf_run_results_raw_12_2026
```{r}
write.csv(df, file = here("data", "raw", "hbf_run_results_raw_12_2026.csv"), row.names = FALSE)
```

Run to obtain df from data folder
```{r}
df <- read.csv(file = here("data", "raw", "hbf_run_results_raw_12_2026.csv"))
```

## Data cleaning
### Remove unnecessary columns
```{r}
names(df) <- make.unique(names(df))
df <- df%>%
  select(-c(Fav, Share, `Name...6`, `Name...7`, `Time(Net Time)`, `Cat Pos(Gen Pos)` ))
```

Renaming some columns -> Removing spaces
Making place, pace and position more meaningful for certain intervals (i.e. 8.6 denotes that was the pace taken at 8.6km).
```{r}
df <- df%>%
  rename(Net_Pos = `Net Pos`,
         Race_No = `Race No`,
         Net_Time = `Net Time`,
         Cat_Pos = `Cat Pos`,
         Net_Cat_Pos = `Net Cat Pos`,
         Time_Behind_Cat = `Time Behind Cat`,
         Gen_Pos = `Gen Pos`,
         Net_Gen_Pos = `Net Gender Pos`,
         Pace = `Pace...21`,
         Pace_8.6 = `Pace...24`,
         Pos_8.6 = `O/Pos...25`,
         Cat_Pos_8.6 = `C/Pos...26`,
         Gen_Pos_8.6 = `G/Pos...27`,
         Pace_8.7 = `Pace...29`,
         Pos_8.7 = `O/Pos...30`,
         Cat_Pos_8.7 = `C/Pos...31`,
         Gen_Pos_8.7 = `G/Pos...32`,
         Pace_9.9 = `Pace...34`,
         Pos_9.9 = `O/Pos...35`,
         Cat_Pos_9.9 = `C/Pos...36`,
         Gen_Pos_9.9 = `G/Pos...37`,
         Pace_12 = `Pace...39`,
         Pos_12 = `O/Pos...40`,
         Cat_Pos_12 = `C/Pos...41`,
         Gen_Pos_12 = `G/Pos...42`,)
```

In our analysis, we're only looking at those who completed the race. In this case, we are removing those who don't have a finishing position. These are runners who didn't start/finish the race.
```{r}
df <- df%>%
  filter(!is.na(Pos))
```

Converting columns into the correct datatypes.
```{r}
df <- df%>%
  mutate(
    Net_Time = as_hms(Net_Time),
    Net_Time_s = as.numeric(Net_Time),
    Time_Behind_Cat = na_if(Time_Behind_Cat, "") |> as_hms(),
    Time_Behind_Cat_s = as.numeric(Net_Time),
    Finish_12km = as_hms(`Finish 12km`),
    Finish_12km_s = as.numeric(Finish_12km),
    Causeway_9.9km = na_if(`Causeway 9.9km`, "") |> as_hms(),
    Causeway_9.9km_s = as.numeric(Causeway_9.9km),
    SpecSprint_8.7km = na_if(`SpecSprint 8.7km`, "") |> as_hms(),
    SpecSprint_8.7km_s = as.numeric(SpecSprint_8.7km),
    SpecStart_8.6km = na_if(`SpecStart 8.6km`, "") |> as_hms(),
    SpecStart_8.6km_s = as.numeric(SpecStart_8.6km),
    Gender = as.factor(Gender),
    Category = as.factor(Category),
    Wave = as.factor(Wave)
  )
```

Making a new variable for wave number, selects exclusively the wave number (i.e. Green Wave (A) becomes A).
```{r}
df <- df%>%
  mutate(Wave_Num = factor(str_sub(Wave, -2, -2)))
```

Saving df in the data folder for later use
```{r}
write.csv(df, file = here("data", "raw", "hbf_run_results_modified_12_2026.csv"), row.names = FALSE)
```

Run to obtain df from data folder
```{r}
df <- read.csv(file = here("data", "raw", "hbf_run_results_modified_12_2026.csv"))
```

# Plot theme
Creating a theme for consistent graphs. 
```{r}
# HBF colours -> for consistent plotting
hbf_col1 <- "#003a5d"
hbf_col2 <- "#00B0BA"
hbf_col3 <- "91D3D0"

hbf_theme <- function(){   #Title
  # Set base theme and font family ---------------------------------------------
  theme_minimal(
    #base_family = "Libre Franklin"
  ) +
    theme(
      # Text elements ----------------------------------------------------------
      plot.title = element_text(
        size = 18,
        face = "bold",
        color = "#333333",
        margin = margin(b = 10)
      ),
      plot.subtitle = element_text(
        size = 14,
        color = "#999999",
        margin = margin(b = 10)
      ),
      plot.caption = element_text(
        size = 13,
        color = "#777777",
        margin = margin(t = 15),
        hjust = 0
      ),
      axis.text = element_text(
        size = 11,
        color = "#333333"
      ),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      # Line elements ----------------------------------------------------------
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(
        linetype = "dashed",
        linewidth = 0.15,
        color = "#999999"
      ),
      panel.grid.major.x = element_blank(),
      axis.ticks.x = element_line(
        linetype = "solid",
        linewidth = 0.25,
        color = "#999999"
      ),
      axis.ticks.length.x = unit(4, units = "pt"),
      # Legend elements --------------------------------------------------------
      legend.position = "bottom"
    )
}
  
```

# Exploratory analysis
Investigating what our df includes. 

```{r}
str(df)
```
Things to note: there are 4 gender types and 13 category types

### Investigating count of gender type

```{r}
ggplot(df, aes(x = Gender))+
  geom_bar(fill = hbf_col2,
                 color = 'white')+ 
  labs(
    title = "Number of finishers by gender - HBF Run 12km",
    subtitle = 'Results from the 2026 HBF Run for a Reason',
    caption = 'Data source: BlueChip results',
    x = 'Gender',
    y = 'Number of finishers')+
  geom_text(
    aes(label = after_stat(count)),
    stat = "count",
    vjust = -0.1,
    color = 'black'
  )+
  hbf_theme()
```
There were 15,448 participants. The majority of runners are female, with 41.5% of runners being male and 33 being Nonbinary and Undisclosed.


### Investigating count of category type. 

Getting category types in the correct order

```{r}
unique(df$Category)
```
Ordering categories for graphing
```{r}
cat_order = c("3 & Under", 
              "12 & Under", 
              "13-15", 
              "16-19", 
              "20-29", 
              "30-39", 
              "40-49", 
              "50-59", 
              "60-69", 
              "70-79", 
              "80 & Over", 
              "Wheelchair", 
              "Unknown")

df$Category <- factor(df$Category,
                      levels = cat_order)
```



```{r}
  
ggplot(df, aes(x = Category))+
  geom_bar(aes(x = factor(Category, cat_order)),
    fill = hbf_col3,
                 color = 'white')+ 
  labs(
    title = "Number of finishers by category - HBF Run 12km",
    subtitle = 'Results from the 2026 HBF Run for a Reason',
    caption = 'Data source: BlueChip results',
    x = 'Gender',
    y = 'Number of finishers')+
  scale_x_discrete(
    labels = function(x) str_wrap(x, width=5)
  )+
  geom_text(
    aes(label = after_stat(count)),
    stat = "count",
    vjust = -0.1,
    color = 'black'
  )+
  hbf_theme()
```
```{r}
  
ggplot(df, aes(y = Category))+
  geom_bar(aes(y = factor(Category, rev(cat_order))),
    fill = hbf_col3,
                 color = 'white')+ 
  labs(
    title = "Number of finishers by category - HBF Run 12km",
    subtitle = 'Results from the 2026 HBF Run for a Reason',
    caption = 'Data source: BlueChip results',
    x = 'Gender',
    y = 'Number of finishers')+
  geom_text(
    aes(label = after_stat(count)),
    hjust = -0.1,
    stat = "count",
    color = 'black'
  )+
  hbf_theme()
```
The vast majority of finishers are in the 20-29 age bracket. There are some categories which have a small amount of finishers, notably 3 & Under, 80 & Over, Wheelchair, Unknown and less prominently, 70-79. 

We'll keep these categories in for now but will note the small quantity of results associated with them. Specifically, 3 & Under where one could infer that parents would help them complete the race. 

### Plotting results against finisher times

Simple plot of all results
```{r}
ggplot(df, aes(x = Net_Time_s))+
  geom_histogram(fill = hbf_col1,
                 color = 'white',
                 binwidth = 300)+ # There is a new bin every five minutes
  scale_x_time(labels = scales::label_time("%H:%M:%S"))+
  labs(
    title = "Distribution of HBF Run 12km results",
    subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
    caption = 'Data source: BlueChip results',
    x = 'Net time',
    y = 'Number of results')+
  hbf_theme()
```
Initial suggestions could lead to bimodallity of the data. 

Creating a similar graph, just for female finishers
```{r}
df%>%
  filter(Gender == "Female")%>%
  ggplot(aes(x = Net_Time_s))+
    geom_histogram(fill = hbf_col2,
                   color = 'white',
                   binwidth = 300)+ # There is a new bin every five minutes
    scale_x_time(labels = scales::label_time("%H:%M:%S"))+
    labs(
      title = "Distribution of female HBF Run 12km results",
      subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
      caption = 'Data source: BlueChip results',
      x = 'Net time',
      y = 'Number of results')+
    hbf_theme()
```

Creating the graphs above but faceted by gender. 
```{r}
df%>%
  ggplot(aes(x = Net_Time_s))+
    geom_histogram(fill = hbf_col2,
                   color = 'white',
                   binwidth = 300)+ # There is a new bin every five minutes
  facet_wrap(~Gender, scales = "free_y")+
    scale_x_time(labels = scales::label_time("%H:%M:%S"))+
    labs(
      title = "Distribution of HBF Run 12km results by gender",
      subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
      caption = 'Data source: BlueChip results',
      x = 'Net time',
      y = 'Number of results')+
    hbf_theme()
```
This shows that males trend to have a faster finisher time than females. They also have a less severe bimodality. It's unclear if this is due to less finishers walking throughout the race or a baseline faster run time. 

Nonbinary and Undisclosed finisher times vary greatly due to the small number of results. 

Creating the graphs above but faceted by category 
```{r}
df%>%
  ggplot(aes(x = Net_Time_s))+
    geom_histogram(fill = hbf_col2,
                   color = 'white',
                   binwidth = 300)+ # There is a new bin every five minutes
  facet_wrap(~Category, scales = "free_y")+
    scale_x_time(labels = scales::label_time("%H:%M:%S"))+
    labs(
      title = "Distribution of HBF Run 12km results by category",
      subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
      caption = 'Data source: BlueChip results',
      x = 'Net time',
      y = 'Number of results')+
    hbf_theme()
```
Results vary greatly depending on age category. 

```{r eval=FALSE, include=FALSE}
# Loop to create separate bar graphs by category and gender (not used)
genders <- unique(df$Gender)
categories <- unique(df$Category)
for (i in genders){
  for (j in categories){
    p <- df%>%
    filter(Gender == i & Category == j)%>%
    ggplot(aes(x = Net_Time_s))+
      geom_histogram(fill = hbf_col2,
                     color = 'white',
                     binwidth = 300)+ # There is a new bin every five minutes
      scale_x_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
        title = "Distribution of HBF Run 12km results",
        subtitle = paste(i, j),
        caption = 'Data source: BlueChip results',
        x = 'Net time',
        y = 'Number of results')+
      hbf_theme()
    print(p)
  }
}

```

### Plotting results against nominated waves

Violin plot of finisher times based on nominated waves
```{r}
df%>%
  ggplot(aes(x=Wave_Num, y=Net_Time_s, fill = Wave_Num))+
  geom_violin()+
  scale_y_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
      title = "Distribution of HBF Run 12km results by wave",
      subtitle = 'Results from the 2026 HBF Run for a Reason separated by starting wave',
      caption = 'Data source: BlueChip results',
      fill = 'Wave number',
      x = 'Wave number',
      y = 'Net time')+
  hbf_theme()
```
This shows that there is a large variety of finisher times, no matter what wave was selected. Wave A and B have a large concentration around the recommended time. Wave C appears to have more consistent times recorded and waves D and E have different distributions but Wave D has a larger concerntration at a slower time which is unexpected given it's not the slowest wave. 

### Plotting results against gender and category

Filtering out genders and categories with small count numbers

```{r}
df%>%
  filter(Gender != "Undisclosed" & Gender != "Nonbinary" & Category != "Wheelchair" & Category != 'Unknown' & Category != '3 & Under')%>%
  group_by(Gender, Category)%>%
  summarise(Count = n(), .groups = "drop_last")%>%
  ggplot(aes(x = Category,
             y = Count,
             fill = Gender))+
  geom_bar(color = 'white',
           stat = 'identity',
           position=position_dodge())+ # There is a new bin every five minutes
      labs(
        title = "HBF Run 12km participants by age group",
        subtitle = "Separated by gender",
        caption = 'Data source: BlueChip results',
        x = 'Age group',
        y = 'Number of runners')+
      hbf_theme()
```

### Summary statistics

Summary statistics - overall
```{r}
df%>%
  summarise(Count = n(),
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```



Summary statistics - separated by gender and category
```{r}
df%>%
  group_by(Gender, Category)%>%
  summarise(Count = n(),
            .groups = "drop_last",
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```

## Gaussian Mixture Modelling 

For summary outputs, it would be helpful to differentiate 'Walking' from 'Running'

Can't separate by waves given there are walkers and runners in the incorrect waves. 

Gaussian Mixture Model (GMM)
(theoreticially could use k-means however, this assigns binary yes/no clusters. In the case of our example, whether a participant walked or ran isn't always binary as they can walk and run for a segment of the race. )

```{r}
gmm <- Mclust(df$Net_Time, G = 2) #G = 2 because we have runners and walkers (i.e. two groups)
gmm_all <- Mclust(df$Net_Time) #Wanting to compare the number of components
gmm_all_log <- Mclust(log(df$Net_Time_s)) #Wanting to compare the number of components
gmm_two_log <- Mclust(log(df$Net_Time_s), G = 2) #Wanting to compare the number of components
summary(gmm_all_log)
```

Investigating both gmm models created, using the log of net time and regular net time. 
```{r}
plot(gmm_all, what = 'BIC')
plot(gmm_all_log, what = 'BIC')
```
To determine the preferred model, BIC would be minimised. 
E denotes if all 'groups' have the same spread whereas V denotes if all 'groups' have different spreads (which is the case for us). 

The log model is a much better fit, given that BIC is minimised for all number of components. 
Furthermore, as suspected, two appears to be the correct number of components. 

```{r}
plot(gmm_all_log, what = 'density')
```
```{r}
summary(gmm_all_log$uncertainty)
```

We are looking for the LOWEST uncertainty value. Given that uncertainty is 1-max(P(cluster))

In the logged median, a median of 0.01 means that most observations are classified with ~99% probability. However, there are some which are struggling to be scaled given that the max is relatively high (these could be runners who also walk sometimes)

```{r}
table(gmm_all_log$classification)
```

Clusters are not evenly split but let's see what this actually means. 
```{r}
df$cluster <- gmm_all_log$classification
```

```{r}
df%>%
  ggplot(aes(x = Net_Time_s,
         fill = factor(cluster)))+
    geom_histogram(
                   color = 'white',
                   binwidth = 300)+ # There is a new bin every five minutes
    scale_x_time(labels = scales::label_time("%H:%M:%S"))+
    labs(
      title = "Distribution of HBF Run 12km results - Separated into two groups",
      subtitle = 'Using a log clustering with a cut off of two clusters. Currently uses hard cut off',
      caption = 'Data source: BlueChip results',
      fill = "Cluster",
      x = 'Net time',
      y = 'Number of results')+
    hbf_theme()
```

Let's look at some summary statistics from these clusters

```{r}
df%>%
  group_by(cluster)%>%
  summarise(Count = n(),
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```

Summary stats by wave and cluster
```{r}
df%>%
  group_by(cluster, Wave_Num)%>%
  summarise(Count = n(),
            .groups = "drop_last",
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```


```{r}
df%>%
  ggplot(aes(x=Wave_Num, y=Net_Time_s, fill = factor(cluster)))+
  geom_boxplot()+
  scale_y_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
      title = "Distribution of HBF Run 12km results by wave",
      subtitle = 'Results from the 2026 HBF Run for a Reason separated by starting wave',
      caption = 'Data source: BlueChip results',
      x = 'Wave number',
      y = 'Net time')+
  hbf_theme()
```

```{r}
df%>%
  ggplot(aes(x=Gender, y=Net_Time_s, fill = factor(cluster)))+
  geom_boxplot()+
  scale_y_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
      title = "Distribution of HBF Run 12km results by wave",
      subtitle = 'Results from the 2026 HBF Run for a Reason separated by starting wave',
      caption = 'Data source: BlueChip results',
      x = 'Wave number',
      y = 'Net time')+
  hbf_theme()
```

```{r}
df%>%
  group_by(cluster, Gender)%>%
  summarise(Count = n(),
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```

Looking to see what factors could be associated with walkers (i.e. cluster = 2)

```{r}
fit <- glm(
  I(cluster == "2") ~ Category + Gender + Wave_Num,
  family = binomial,
  data = df
)
```

```{r}
summary(fit)
```
**** NOTE TO JEMMA: Think about that a little further

# Looking at wave numbers

Green wave (1) -> 50mins - 1h 10mins
Brown wave (2) -> 1h 10mins - 1h 25mins
Purple wave (3) -> 1h 25mins - 1h 40mins
Pink wave (4) -> 1h 40mins - 2h
Sky blue wave (5) -> 2h +

```{r}
wave_times <- list(
  A = c(as_hms(00:50:00), as_hms(01:10:00)),
  B = c(as_hms(01:10:00), as_hms(01:25:00)),
  C = c(as_hms(01:25:00), as_hms(01:40:00)),
  D = c(as_hms(01:40:00), as_hms(02:00:00)),
  E = c(as_hms(02:00:00), NA)
)
```


Dividing the number of results by 5 (to see what the threshold should theoreticially be)

```{r}
df%>%
  summarise(`Wave 1` = strftime(as_hms(quantile(Net_Time_s, probs = c(0.2))), "%H:%M:%S"),
            `Wave 1 count` = sum(Net_Time<= `Wave 1`, na.rm = TRUE),
            `40%` = strftime(as_hms(quantile(Net_Time_s, probs = c(0.4))), "%H:%M:%S"),
            `60%` = strftime(as_hms(quantile(Net_Time_s, probs = c(0.6))), "%H:%M:%S"),            
        `80%` = strftime(as_hms(quantile(Net_Time_s, probs = c(0.8))), "%H:%M:%S"),
        `100%` = strftime(as_hms(quantile(Net_Time_s, probs = c(0.1))), "%H:%M:%S"))
                                                      
                

```


```{r}
qs <- quantile(df$Net_Time_s,
               probs = seq(0, 1, 0.2),
               na.rm = TRUE)

df %>%
  summarise(
    `Wave 1` = strftime(as_hms(qs[1]), "%H:%M:%S"),
    `Wave 1 count` = sum(Net_Time_s <= qs[1], na.rm = TRUE),
    `Wave 2` = strftime(as_hms(qs[2]), "%H:%M:%S"),
    `Wave 2 count` = sum(Net_Time_s <= qs[2] & Net_Time_s > qs[1], na.rm = TRUE),
    `Wave 3` = strftime(as_hms(qs[3]), "%H:%M:%S"),
    `Wave 3 count` = sum(Net_Time_s <= qs[3] & Net_Time_s > qs[2], na.rm = TRUE),
    `Wave 4` = strftime(as_hms(qs[4]), "%H:%M:%S"),
    `Wave 4 count` = sum(Net_Time_s <= qs[4] & Net_Time_s > qs[3], na.rm = TRUE),
    `Wave 5` = strftime(as_hms(qs[5]), "%H:%M:%S"),
    `Wave 5 count` = sum(Net_Time_s <= qs[4] & Net_Time_s > qs[4], na.rm = TRUE),
    `Wave 6` = strftime(as_hms(qs[6]), "%H:%M:%S"),
    `Wave 6 count` = sum(Net_Time_s > qs[5], na.rm = TRUE),
  )
```

Wave cut-offs are almost correct as to what was published. 

so.... how many people overestimated or underestimated their skills?















