---
title: "HBF run analysis"
output: html_document
date: "2026-05-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing packages
```{r}
install.packages('mclust')
```

## Importing libraries

```{r library, include=FALSE}
library(readr)
library(RCurl)
library(here) # To reference files inside R Project
library(tidyverse)
library(rvest)
library(dplyr)
library(hms)
library(hrbrthemes)
library(ggridges)
library(mclust)
```

## Scraping the data from the results website

```{r}
pages <- list()
url_pre <- "https://bluechipresults.com.au/results.aspx?CId=11&RId=1975&EId=1&dt=0&PageNo="
for (i in 1:360){
  url <- paste(url_pre, i, sep = "")
  print(url)
  popNodes <- html_nodes(read_html(url), "table")
  pop <- html_table(popNodes, header = TRUE, fill = TRUE)[[2]]
  pages[[i]] <- pop
  
}

df <- bind_rows(pages)
```

Saving df for later usage
```{r}
write.csv(df, file = here("data", "raw", "hbf_run_results_raw_12_2025.csv"), row.names = FALSE)
```


## Data cleaning
### Remove unnecessary columns
```{r}
names(df) <- make.unique(names(df))
df <- df%>%
  select(-c(Fav, Share, `Name...6`, `Name...7`, `Time(Net Time)`, `Cat Pos(Gen Pos)` ))
```

Renaming some columns
```{r}
df <- df%>%
  rename(Net_Pos = `Net Pos`,
         Race_No = `Race No`,
         Net_Time = `Net Time`,
         Cat_Pos = `Cat Pos`,
         Net_Cat_Pos = `Net Cat Pos`,
         Time_Behind_Cat = `Time Behind Cat`,
         Gen_Pos = `Gen Pos`,
         Net_Gen_Pos = `Net Gender Pos`,
         Pace = `Pace...19`,
         Pace_8.6 = `Pace...22`,
         Pos_8.6 = `O/Pos...23`,
         Cat_Pos_8.6 = `C/Pos...24`,
         Gen_Pos_8.6 = `G/Pos...25`,
         Pace_8.7 = `Pace...27`,
         Pos_8.7 = `O/Pos...28`,
         Cat_Pos_8.7 = `C/Pos...29`,
         Gen_Pos_8.7 = `G/Pos...30`,
         Pace_9.9 = `Pace...32`,
         Pos_9.9 = `O/Pos...33`,
         Cat_Pos_9.9 = `C/Pos...34`,
         Gen_Pos_9.9 = `G/Pos...35`,
         Pace_12 = `Pace...37`,
         Pos_12 = `O/Pos...38`,
         Cat_Pos_12 = `C/Pos...39`,
         Gen_Pos_12 = `G/Pos...40`,)
```


Needs to remove rows with null times
```{r}
df <- df%>%
  filter(!is.na(Pos))
```

Need to convert all columns into the correct type
```{r}
df <- df%>%
  mutate(
    Net_Time = as_hms(Net_Time),
    Net_Time_s = as.numeric(Net_Time),
    Time_Behind_Cat = na_if(Time_Behind_Cat, "") |> as_hms(),
    Time_Behind_Cat_s = as.numeric(Net_Time),
    Finish_12km = as_hms(`Finish 12km`),
    Finish_12km_s = as.numeric(Finish_12km),
    Causeway_9.9km = na_if(`Causeway 9.9km`, "") |> as_hms(),
    Causeway_9.9km_s = as.numeric(Causeway_9.9km),
    SpecSprint_8.7km = na_if(`SpecSprint 8.7km`, "") |> as_hms(),
    SpecSprint_8.7km_s = as.numeric(SpecSprint_8.7km),
    SpecStart_8.6km = na_if(`SpecStart 8.6km`, "") |> as_hms(),
    SpecStart_8.6km_s = as.numeric(SpecStart_8.6km),
  )
```

Making a new variable for wave
```{r}
df <- df%>%
  mutate(Wave_Num = str_sub(Wave, -2, -2))
```




Creating net time bins to group those in the nearest 10 seconds

plot theme
```{r}
hbf_col1 <- "#003a5d"
hbf_col2 <- "#00B0BA"
hbf_col3 <- "91D3D0"
hbf_theme <- function(){   #Title
  # Set base theme and font family ---------------------------------------------
  theme_minimal(
    #base_family = "Libre Franklin"
  ) +
    # Overwrite base theme defaults --------------------------------------------
  # Primary colour (dark blue): #003a5d
  # Sub colour (medium blue): #2596be
  # Sub colour (light blue/green): #91d3d0
    theme(
      # Text elements ----------------------------------------------------------
      plot.title = element_text(
        size = 18,
        face = "bold",
        color = "#333333",
        margin = margin(b = 10)
      ),
      plot.subtitle = element_text(
        size = 14,
        color = "#999999",
        margin = margin(b = 10)
      ),
      plot.caption = element_text(
        size = 13,
        color = "#777777",
        margin = margin(t = 15),
        hjust = 0
      ),
      axis.text = element_text(
        size = 11,
        color = "#333333"
      ),
      plot.title.position = "plot",
      plot.caption.position = "plot",
      # Line elements ----------------------------------------------------------
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(
        linetype = "dashed",
        linewidth = 0.15,
        color = "#999999"
      ),
      panel.grid.major.x = element_blank(),
      axis.ticks.x = element_line(
        linetype = "solid",
        linewidth = 0.25,
        color = "#999999"
      ),
      axis.ticks.length.x = unit(4, units = "pt"),
      # Legend elements --------------------------------------------------------
      legend.position = "bottom"
    )
}
  
```



Simple plot of all results
```{r}
ggplot(df, aes(x = Net_Time_s))+
  geom_histogram(fill = hbf_col1,
                 color = 'white',
                 binwidth = 300)+ # There is a new bin every five minutes
  scale_x_time(labels = scales::label_time("%H:%M:%S"))+
  labs(
    title = "Distribution of HBF Run 12km results",
    subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
    caption = 'Data source: BlueChip results',
    x = 'Net time',
    y = 'Number of results')+
  hbf_theme()
```

```{r}
df%>%
  filter(Gender == "Female")%>%
  ggplot(aes(x = Net_Time_s))+
    geom_histogram(fill = hbf_col2,
                   color = 'white',
                   binwidth = 300)+ # There is a new bin every five minutes
    scale_x_time(labels = scales::label_time("%H:%M:%S"))+
    labs(
      title = "Distribution of female HBF Run 12km results",
      subtitle = 'Results from the 2026 HBF Run for a Reason shown in 5 minute intervals',
      caption = 'Data source: BlueChip results',
      x = 'Net time',
      y = 'Number of results')+
    hbf_theme()
```


```{r}
genders <- unique(df$Gender)
categories <- unique(df$Category)
for (i in genders){
  for (j in categories){
    p <- df%>%
    filter(Gender == i & Category == j)%>%
    ggplot(aes(x = Net_Time_s))+
      geom_histogram(fill = hbf_col2,
                     color = 'white',
                     binwidth = 300)+ # There is a new bin every five minutes
      scale_x_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
        title = "Distribution of HBF Run 12km results",
        subtitle = paste(i, j),
        caption = 'Data source: BlueChip results',
        x = 'Net time',
        y = 'Number of results')+
      hbf_theme()
    print(p)
  }
}

```

Boxplot for categories
```{r}
genders <- unique(df$Gender)
categories <- unique(df$Category)
for (i in genders){
  for (j in categories){
    p <- df%>%
    filter(Gender == i & Category == j)%>%
    ggplot(aes(y=Net_Time_s))+
      geom_boxplot()+
      scale_y_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
        title = "Distribution of HBF Run 12km results",
        subtitle = paste(i, j),
        caption = 'Data source: BlueChip results',
        x = 'Net time',
        y = 'Number of results')+
      hbf_theme()
    print(p)
  }
}

```



Boxplot
```{r}
df%>%
  ggplot(aes(x=Wave_Num, y=Net_Time_s, fill = Wave_Num))+
  geom_violin()+
  scale_y_time(labels = scales::label_time("%H:%M:%S"))+
      labs(
      title = "Distribution of HBF Run 12km results by wave",
      subtitle = 'Results from the 2026 HBF Run for a Reason separated by starting wave',
      caption = 'Data source: BlueChip results',
      x = 'Wave number',
      y = 'Net time')+
  hbf_theme()
```
```{r}
df%>%
  filter(Gender != "Undisclosed" & Gender != "Nonbinary" & Category != "Wheelchair" & Category != 'Unknown' & Category != '3 & Under')%>%
  group_by(Gender, Category)%>%
  summarise(Count = n())%>%
  ggplot(aes(x = Category,
             y = Count,
             fill = Gender))+
  geom_bar(color = 'white',
           stat = 'identity',
           position=position_dodge())+ # There is a new bin every five minutes
      labs(
        title = "HBF Run 12km participants by age group",
        subtitle = "Separated by gender",
        caption = 'Data source: BlueChip results',
        x = 'Age group',
        y = 'Number of runners')+
      hbf_theme()
```
Summary stats - overall
```{r}
df%>%
  summarise(Count = n(),
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```



Summary stats - grouped
```{r}
df%>%
  group_by(Gender, Category)%>%
  summarise(Count = n(),
            Mean = strftime(as_hms(mean(Net_Time_s)), "%H:%M:%S"),
            Median = strftime(as_hms(median(Net_Time_s)), "%H:%M:%S"),
            Min = strftime(as_hms(min(Net_Time_s)), "%H:%M:%S"),
            Max = strftime(as_hms(max(Net_Time_s)), "%H:%M:%S"),
            `25%` = strftime(as_hms(quantile(Net_Time_s)[2]), "%H:%M:%S"),
            `75%` = strftime(as_hms(quantile(Net_Time_s)[4]), "%H:%M:%S"),
            `SD` = strftime(as_hms(sd(Net_Time_s)), "%H:%M:%S"))
```

For summary outputs, it would be helpful to differentiate 'Walking' from 'Running'

Can't separate by waves given there are walkers and runners in the incorrect waves. 

Gaussian Mixture Model (GMM)
(theoreticially could use k-means however, this assigns binary yes/no clusters. In the case of our example, whether a participant walked or ran isn't always binary as they can walk and run for a segment of the race. )

```{r}
gmm <- Mclust(df$Net_Time, G = 2) #G = 2 because we have runners and walkers (i.e. two groups)
gmm_all <- Mclust(df$Net_Time) #Wanting to compare the number of components
summary(gmm)
```

```{r}
plot(gmm, what = 'BIC')
```


```{r}
plot(gmm, what = 'density')
```


